Hierarchical Dispatching and Overriding

### 2017-06-19 Aplas17/sections/Conclusion.tex
Finish one round of review.

This paper proposes \MIM{} as a new multiple inheritance model for unintentional method conflicts.
Existing approaches including static dispatch and dynamic dispatch have to compromise between code reuse
and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
Such an approach not only offers great code reuse like dynamic dispatch, but also ensures unambiguity by
our algorithm for method resolution. This paper also introduces method updates for refinements on branches individually.
\MIM{} is formalized with a basis on Featherweight Java, and supported
by a few theorems. The prototype is implemented in Scala as a simple interpreter.

>>>>

This paper proposes \MIM{} as a new multiple inheritance model for unintentional method conflicts.
Existing approaches including static dispatch and dynamic dispatch have to compromise between code reuse
and type safety, whereas \MIM{} uses a different solution called hierarchical dispatch to obtain both.
Such an approach not only offers great code reuse like dynamic dispatch but also ensures unambiguity by
our algorithm for method resolution. This paper also introduces hierarchical overriding that refines branches individually.
\MIM{} is formalized with a basis on Featherweight Java and supported
by a few theorems. The prototype is implemented in Scala as a simple interpreter.
